{Automatic Least-Effort Contextual Learning}

### 2017-02-24 etc/paper.tex
for paper, s/evaluation metrics/experiments/

\section{Evaluation Metrics}

\begin{figure}[h]
\centering
\includegraphics[scale=.5]{exps.eps}
\caption{Domains for test experiments. Items in each of these three domains
  have substructures of modular concepts which are useful across many tasks,
  making them fitting domains to utilize contextual knowledge.}
\label{fig:exps}
\end{figure}

@@

We augment an algorithm which performs search on a learned expressive
grammar, the EC algorithm \cite{dechter13}. The augmentation will define the
grammar based on learned language artifacts stored in the context, rather
than artifacts stored in a small bounded set. The modified EC algorithm will
be tested in the domains of letter analogies \cite{hofstadter94}, L-systems
\cite{rozenberg80}, and Boolean circuits illustrated in Figure
\ref{fig:exps}. These problem domains were chosen because they each have
potential for common underlying structure between tasks. Results will be
compared to the original EC algorithm on number of tasks solved given number
of iterations for the algorithm.

>>>>

\section{Experiments}

@@

We augment an algorithm which performs search on a learned expressive
grammar, the EC algorithm \cite{dechter13}. The augmentation will define the
grammar based on learned language artifacts stored in the context, rather
than artifacts stored in a small bounded set. The augmented EC algorithm
will be tested in the domain of string transformation, chosen because it has
potential for common underlying structure between tasks. Results will be
compared to the original EC algorithm.

This section is very much {\bf TODO}.
